---
title: "Individual assingment wb"
author: "Hira Piracha"
date: "11/23/2019"
output: html_document
---

```{r}
#loading libraries
library(rvest)
library(data.table)
```

```{r}
my_page_number <- 1:3
page_to_download <- 3
my_base_url <- paste0("https://www.economist.com/books-and-arts/?page=", my_page_number)

```

dataframe of one page

```{r}

get_one_page <- function(my_base_url){
  
  t <- read_html(my_base_url)

  my_titles <- 
  t %>%
  html_nodes('.flytitle-and-title__flytitle')%>%
  html_text()

  my_links <- 
  t %>%
  html_nodes('.flytitle-and-title__title')%>%  
  html_text('href')
  
  
  my_summary <- 
  t %>%
  html_nodes('.teaser__text')%>%
  html_text()

  return(data.frame('titles' = my_titles, 'links'= my_links, 'summary' = my_summary))
}

#make the url
first_link <- ("https://www.economist.com/books-and-arts/")

#res
rest_link <- paste0("https://www.economist.com/books-and-arts/?page=", c(2:page_to_download))

my_links<- c(first_link, rest_link)

df_lists  <- lapply(my_links, get_one_page)

final_df <- rbindlist(df_lists)

#view the final table
head(final_df)

```



final_df <- rbindlist(df_lists)



# it is nicer if your df is comming for every search result box 

get_one_page_from_boxes <- function(my_base_url) {
  
  # make dataframe of one page
  t <- read_html(my_base_url)
  res_boxes <- t %>%
    html_nodes('#content li')
  
  res_boxes <- res_boxes[1:10]
  
list_of_boxes_df <- 
  lapply(res_boxes, function(x){
    my_titles <- 
      x %>%
      html_nodes('a')%>%
      html_text()
    
    my_links <- 
      x %>%
      html_nodes('a')%>%
      html_attr('href')
    
    my_summary <- 
      x %>%
      html_nodes('p')%>%
      html_text()
    
    return(data.frame('titles' = my_titles, 'links'= my_links, 'summary' = my_summary))
  })

  
df_of_the_page <- rbindlist(list_of_boxes_df) 

return(df_of_the_page )  
}

# we can use the same links

df_lists  <- lapply(my_links, get_one_page_from_boxes)

final_df <- rbindlist(df_lists)

saveRDS(final_df, 'base_excersise/data_res.rds')
